### 2020-06-29 2020/WCGO_MCO_OptimizationLetters/2020_WCGO_MCO.tex
one correction

\begin{theorem}
Let the next minimized function $\psi(x)$ of the computational scheme (\ref{eq:9}) differ from the previous minimized function $\phi(x)$ by some limited value $\delta$, i.e.
\begin{equation}\label{eq:32}
|\psi(x)-\phi(x)| \leq \delta, x \in [0,1],
\end{equation}
and let the stopping criterion of (\ref{eq:28}) for the specified accuracy of global search $\varepsilon>0$ be fulfilled when minimizing the function $\phi(x)$. Then 
\begin{equation}\label{eq:33}
|\psi(x^*)-\phi(x_k^*)| \leq \Delta = \frac{\alpha L \varepsilon}{2} + \delta,
\end{equation}
if starting from a certain iteration $k_0>0$ the condition is fulfilled for the estimation of the Lipschitz constant $m$ and some $\alpha > 1$
\begin{equation}\label{eq:34}
m \geq L (1+ \sqrt{\frac{\alpha + 4 \beta (1 + \beta)}{\alpha - 1}}),
\end{equation}
where
\begin{equation}\label{eq:35}
m=\max{r_l H_l^k}, 1 \leq l \leq M^k, k>k_0,
\end{equation}
\begin{equation}\label{eq:36}
L=\max{L_i}, 1 \leq i \leq s, L_i\; \text{from}\; (\ref{eq:3}),
\end{equation}
\begin{equation}\label{eq:37}
\psi(x^*)=\min{\psi(x)},x \in [0,1],
\end{equation}
\begin{equation}\label{eq:38}
x_k^* = arg \min{\phi(x_k)}, 1 \leq i \leq k.
\end{equation}
\end{theorem}
The points $x_k$, $1 \leq i \leq k$, in (\ref{eq:38}) are taken from search information $A_k$ from (\ref{eq:21}) obtained by minimizing the function $\phi(x)$, and $H_l^k$, $M^k$, $r_l$ are the values of (\ref{eq:22}), (\ref{eq:24}) and (\ref{eq:29}), respectively.

>>>>

\begin{theorem}
Let the next minimized function $\psi(x)$ of the computational scheme (\ref{eq:9}) differs from the previous minimized function $\phi(x)$ by some limited value $\delta$, i.e.
\begin{equation}\label{eq:32}
|\psi(x)-\phi(x)| \leq \delta, x \in [0,1],
\end{equation}
and let the stopping criterion of (\ref{eq:28}) for the specified accuracy of global search $\varepsilon>0$ be fulfilled when minimizing the function $\phi(x)$. Then 
\begin{equation}\label{eq:33}
|\psi(x^*)-\phi(x_k^*)| \leq \Delta = \frac{\alpha L \varepsilon}{2} + \delta,
\end{equation}
if starting from a certain iteration $k_0>0$ the condition is fulfilled for the estimation of the Lipschitz constant $m$ and some $\alpha > 1$
\begin{equation}\label{eq:34}
m \geq L (1+ \sqrt{\frac{\alpha + 4 \beta (1 + \beta)}{\alpha - 1}}),
\end{equation}
where
\begin{equation}\label{eq:35}
m=\max{r_l H_l^k}, 1 \leq l \leq M^k, k>k_0,
\end{equation}
\begin{equation}\label{eq:36}
L=\max{L_i}, 1 \leq i \leq s, L_i\; \text{from}\; (\ref{eq:3}),
\end{equation}
\begin{equation}\label{eq:37}
\psi(x^*)=\min{\psi(x)},x \in [0,1],
\end{equation}
\begin{equation}\label{eq:38}
x_k^* = arg \min{\phi(x_k)}, 1 \leq i \leq k.
\end{equation}
\end{theorem}
The points $x_k$, $1 \leq i \leq k$, in (\ref{eq:38}) are taken from search information $A_k$ from (\ref{eq:21}) obtained by minimizing the function $\phi(x)$, and $H_l^k$, $M^k$, $r_l$ are the values of (\ref{eq:22}), (\ref{eq:24}) and (\ref{eq:29}), respectively.
